### 2013-07-08 texts/PaperDraft.Rmd
Further writting in the second section.

# Learning Polynomial Regression with Genetic Algorithms

@@

@@

Many applications require models that have no acceptable linear approximation and many nonlinear models are defined by polynomials. The use of genetic algorithms to find the parameters of a polynomial model is decades old but still poses challenges due to the complexity of the search and different definitions of "optimal" solution.
This work describes a general method based in genetic algorithms to find "empirical" polynomial regressions.

@@

With notable exceptions (_e.g._ neural networks), most machine learning regression techniques are based on linear models. This assumption has many advantages including, for example, reduced computational complexity and strong theoretical framework. However nonlinearity in unavoidable in many application scenarions or, _e.g._ in systems with feedback loops so common in ecology, cybernetics, robotics and other areas. Nevertheless the variety and number of phenomena that can be adapted into a linear model is amazing.

@@

The canonical representation of a polynomial is a sum
$$
p\left( x_1, \ldots, x_n\right) = \sum_i \beta_i m_i.
$$

In this sum each $m_i$ is a monomial, $m_i = \prod_{j\in M_i} x_j^{\alpha_{ij}}$, the exponents are non-negative integers, $\alpha_{ij}\in\mathbb{N}_0$, and the coeficients are real valued, $\beta_i \in \mathbb{R}$. For example $p\left( x_1, x_2, x_3 \right) = 2 x_1 + x_2 x_3 + \frac{1}{2} x_1^2 x_3$ has monomials $m_1 = x_1, m_2 = x_2 x_3$ and $m_3 = x_1^2 x_3$ coefficients $\beta_1 = 2, \beta_2 = 1$ and $\beta_3 = 1/2$ and exponents $\alpha_{1,1} = 1, \alpha_{2,2}=1, \alpha_{2,3} = 1, \alpha_{3,1} = 2, \alpha_{3,3} = 1$ and all other $\alpha_{ij} = 0$.

> **NOTA** Este parágrafo deu-me uma ideia: os $\alpha$ definem uma matriz em que as linhas são monómios e as colunas variáveis; "Multiplicando" esta matriz por um vector, obtemos o polinómio. Além disso, podemos continuar a definir a condição de regularização como antes, mas também podemos considerar condições *na* matriz (por exemplo, o número de entradas não nulas ser esparso ou a sua soma ser dominada por $\log nm$)...

@@

1. for a given set of monomials $q_1, \ldots, q_n$, find regression coefficients $\beta_1,\ldots,\beta_n$ that minimize an adequate cost function;
2. find the fittest set of monomials;

@@

Given a dataset $D=\left\lbrace x_1^{(i)}, \ldots, x_m^{(i)}, y^{(i)} \in \mathbb{R}^{m+1} : i = 1,\ldots, n \right\rbrace$ with $n$ observations of $m+1$ variables $X_1, \ldots, X_m, Y$. We want to find a polynomial that fits $y = h\left( x_1, \ldots, x_m\right)$ and for that purpose we apply the usual _root-mean-square error_ as a cost function of a candidate fitting polynomial $h_{\Theta}$ defined by parameters $\Theta$:
$$
J_{fit}\left( \Theta; D \right) = \frac{1}{n} \sum_{i=1}^n \left( y^{(i)} - h_{\Theta}\left(x_1^{(i)}, \ldots, x_m^{(i)}\right) \right)^2
$$

>>>>

# Exploring Polynomial Structure of Data with Genetic Algorithms

@@

>Antes de submeter, temos de considerar [Polynomial regression na wikipedia](http://en.wikipedia.org/wiki/Polynomial_regression) e a [regressão não-linear em geral](https://www.google.pt/search?q=nonlinear+regression).  
>
>Como este trabalho anda no meio de áreas muito trabalhadas, temos de ter muito cuidado com a questão da **investigação original**.

@@

Many applications require models that have no acceptable linear approximation and many nonlinear models are defined by polynomials. The use of genetic algorithms to find polynomial models is decades old but still poses challenges due to the complexity of the search and different definitions of "optimal" solution.
This work describes a general method based in genetic algorithms to find "empirical" polynomial regressions.

@@

With notable exceptions (_e.g._ neural networks), most machine learning regression techniques are based on linear models. This assumption has many advantages including, for example, reduced computational complexity and strong theoretical framework. However nonlinearity in unavoidable in many application scenarions _e.g._ phase transitions or systems with feedback loops so common in ecology, cybernetics, robotics and other areas. Nevertheless the variety and number of phenomena that can be adapted into a linear model is amazing.

@@

The canonical representation of a polynomial is a sum
$$
p\left( x_1, \ldots, x_k\right) = \sum_i \beta_i m_i.
$$

In this sum each $m_i$ is a monomial, $m_i = \prod_{j\in A_i} x_j^{\alpha_{ij}}$, the exponents are non-negative integers, $\alpha_{ij}\in\mathbb{N}_0$, and the coeficients are real valued, $\beta_i \in \mathbb{R}$. For example $p\left( x_1, x_2, x_3 \right) = 2 x_1 + x_2 x_3 + \frac{1}{2} x_1^2 x_3$ has monomials $m_1 = x_1, m_2 = x_2 x_3$ and $m_3 = x_1^2 x_3$ coefficients $\beta_1 = 2, \beta_2 = 1$ and $\beta_3 = 1/2$ and exponents $\alpha_{1,1} = 1, \alpha_{2,2}=1, \alpha_{2,3} = 1, \alpha_{3,1} = 2, \alpha_{3,3} = 1$ and all other $\alpha_{ij} = 0$.

> **NOTA** Este parágrafo deu-me uma ideia: os $\alpha$ definem uma matriz $A$ em que as linhas são monómios e as colunas variáveis; "Multiplicando" esta matriz por um vector, obtemos o polinómio: $P=CA$. Além disso, podemos continuar a definir a condição de regularização como antes, mas também podemos considerar condições *na* matriz (por exemplo, o número de entradas não nulas ser esparso ou a sua soma ser dominada por $\log nm$)...

@@

1. for a given set of monomials $q_1, \ldots, q_r$, find regression coefficients $\theta_1,\ldots,\theta_r$ that minimize an adequate cost function;
2. find the fittest set of monomials;

@@

Given a dataset $D=\left\lbrace x_1^{(i)}, \ldots, x_k^{(i)}, y^{(i)} \in \mathbb{R}^{k+1} : i = 1,\ldots, n \right\rbrace$ with $n$ observations of $k+1$ variables $X_1, \ldots, X_k, Y$. To find a polynomial that fits the observations of the dependent variable $Y$ the usual procedure is to explore parameters $\Theta$ of a polynomial hypothesis $h_{\Theta}$ and select a combination that minimizes the _root-mean-square error_ in the dataset $D$:
$$
J_{fit}\left( \Theta; D \right) = \frac{1}{n} \sum_{i=1}^n \left( y^{(i)} - h_{\Theta}\left(x_1^{(i)}, \ldots, x_m^{(i)}\right) \right)^2
$$

Since it is always possible to fit exactly a polynomial to any given dataset, _overfitting_ the available data, a _regularization_ factor is needed to penalyze hypothesis too biased by the training data:

$$
J_{reg} = ?
$$
